Alleviating the Topology Mismatch Problem in Unstructured and Structured Overlay Networks: A Survey

### 2014-01-21 unstructured.tex
2012.06.11 (Vassilis) Content revisited. Duplicate text has been removed.

%{\sethlcolor{yellow}\hl{
%HA: TALK ABOUT GNUTELLA HERE!!!!}}

@@

\begin{figure}[ht]
\centering
\subfigure[Iterative deepening with three levels.] {
  \includegraphics[scale=0.4]{img/algorithms/iterative_deepening}
  \label{figure:dbfs:iterdeep}
}\qquad\qquad
\subfigure[Directed BFS.] {
  \includegraphics[scale=0.4]{img/algorithms/directed_bfs}
  \label{figure:dbfs:dbfs}
}\qquad\qquad
\subfigure[local indices with radius size equal to $2$.] {
  \includegraphics[scale=0.4]{img/algorithms/local_indices}
  \label{figure:dbfs:localindx}
}
\caption{}
\label{figure:dbfs}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Gia}
\emph{Gia} \cite{chawathe_gia_2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbours, so
that neighbours only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogenity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones. Although
the topology adaptation algorithm Gia uses improves the scalability of the
network, it does not help much in solving the topology mismatch problem, since
it does not consider the underlying physical topology.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Distributed Cycle Minimization Protocol}
We have already mentioned Gnutella's inefficient broadcasting mechanism in
flooding messages across the network with no actual targeting. This leads, to
nodes that are far from the path towards the query request gratification, to
spend their valuable resources to receive, queue and process messages that they
shouldn't have received in the first place and eventually simply forward them
blindly to continue this vicious cycle. Except from that, though, an other case
of wasting network resources is when a node that is on the right path for the
query, receives the same message multiple times from different neighbours. The
reason for these duplicate messages is cycles in the forwarding paths. Actually,
this duplicate packet problem seems to hurt more the active nodes; those with
higher capacities and bandwidth that contribute the most to the network.
Distributed Cycle Minimization Protocol (DCMP) \cite{zhu_dcmp_2008} introduces a
method to
remove the cycles and eliminate the duplicate packets, without sacrificing
overlay connectivity. In DCMP, once a cycle is detected, the most powerful node
in the cycle is elected as the \emph{Gate Peer} and the cycle is then destroyed
by cutting that special link which will result in the minimisation of the
distance to the Gate Peer for all the nodes that participated in that cycle. The
process is managed by using two special message types namely \emph{Information
Collection (IC)} and \emph{Cut Message (CM)}. One disadvantage of DCMP is that
since the distance a forwarded message can travel is limited by the TTL value,
which is practically $7$ in most cases DCMP cannot detect cycles formed by more
than 7 peers. Even though cycle elimination improves the network performance, it
does not actually solve the topology mismatch problem.

@@

@@

Narada \cite{chu_esm_2000,chu_esm_2001,chu_esm_2002} is a generic protocol for
creating self-adapting overlay networks, that can achieve application-layer
multicast communication without requiring IP multicast infrastructure at the
network layer. IP multicast is the term reffering to the method of sending IP
datagrams to a group of receivers in a single transmission. Even though the
method is available some years now, IP multicast has not taken off as
anticipated since many believe that it violates the stateless design of the
current Internet. For this reason it is widely deployed in contained
environments like enterprises (i.e. IPTV applications - distance learning, video
conferencing), commercial stock exchanges, and multimedia content delivery
networks. Narada tries to break these constraints. Although it was not
originally designed as a P2P file sharing protocol, it has become one of the
pioneering works in the overlay networks area. The authors claim that, although
Narada is not as efficient as IP multicast, still it provides reasonable
performance, without the additional cost of implementing multicast services on
the current Internet infrastructure. Additionally, authors realised the
inefficiency caused by the topology mismatch problem and tried to encounter it
by building a richer connected graph, called a mesh, and building per source
minimum spanning trees \footnote{ENarada \cite{li_enarada_2008} used Gossip
protocol for the construction} as shown in Figure~\ref{figure:narada}. They also
keep the graph and the trees dynamically updated while nodes continue to join
and leave the network. Moreover, the protocol tries to ease the physical link
stress, the overall resource usage and the relative delay among end systems.
Unfortunately, the most imporpant limitation of Narada is that although it works
reasonably well for small groups, it does not scale well for larger networks,
therefore it is not suitable for, potentially very large, P2P file sharing
application networks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Adaptive Overlay Topology Optimization and Adaptive Connection
Establishment}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{liu_auto_2003} is one
of the first attempts, along with Narada, from the P2P research community to
address the topology mismatch problem. AOTO is a distributed algorithm that uses
\emph{Selective Flooding} and \emph{Active Topology} to optimize the overlay
network topology. The \emph{Selective Flooding} algorithm creates a minimum
spanning tree over the overlay and uses this tree instead of flooding the whole
network, without shrinking the search scope. In \emph{Active Topology}, the
physical locations of nodes are estimated based on the network delay among them
and physically close nodes are connected as neighbours to revise the overlay
topology as close as possible to the physical network topology. Overall, AOTO
reports a $55\%$ performance improvement in terms of the traffic load. In
\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004}, the authors
extend the idea by introducing optimizations based on the depths of the minimum
spanning trees. But since the network delay is not always a reliable estimation
method to detect the physical location of peers, the algorithm still suffers
from the discrepancies caused by mislocated nodes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Location-aware Topology Matching}
\emph{Location-aware Topology Matching (LTM)} \cite{liu_ltm_2004} proposes a
method to optimize the overlay structure of the P2P network based on the
physical topology. To achieve this, the algorithm issues a special message
called \textit{TTL2-detector} to detect the latency of two-hop neighbours
($N^2$) around each node. The latency information gathered is later used to
evolve the overlay network into a more efficient one, without reducing the
search scope. Each node examines the latency information with the neighbours and
low productive connections are dropped and replaced by more efficient ones, thus
reducing the latency on the overall network, and eliminating some potential
inefficiencies, such as unnecessary crossing of messages over autonomous system
(AS) boundaries, etc. Although LTM improves the overall efficiency of the P2P
network, it does not actually use real physical topology information, just
latency metrics, therefore it does not offer a guaranteed safety net for the
topology mismatch problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Scalable Bipartite Overlay}
\emph{Scalable Bipartite Overlay
(SBO)} \cite{liu_bipartite_IPDPS,liu_bipartite_2007} reduces the overhead of
creating and maintaining a minimum spanning tree cost by randomly dividing the
nodes into two groups, namely red and white and assigning different tasks to
different groups. The white peers measure distances to neighbours by using the
network delay as the metric and reports the results to red peers. The red peers,
equipped with the information of all two-hop neighbours ($N^2$), creates a
minimum spanning tree of these neighbours and assigns efficient forwarding
paths. The white peers can further optimize their positions within the overlay
if this is required.

@@

\hline
\textbf{MAY OMIT- T2MC} &
\textbf{Overlay optimization based} Uses traceroute results for clustering the
nodes  & & \\

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: HOW CAN UNSTRUCTURED SCHEMES BE REFINED
%
%For this reasons, efforts have been placed for optimizing the efficiency of
%decentralized unstructured peer-to-peer networks. Research mainly focuses on
%\begin{inparaenum}[\itshape i\upshape)]
%  \item reducing unnecessary, redundant communication traffic, and
%  \item exploiting physical locality to reduce communication response.
%\end{inparaenum}
%The goal can be achieved at, both, the application-level network as well as the
%underlying physical one. In the first case by refining the message relay
%techniques, while in the second one, by adaptively reconstructing the
%application network to map as well as possible to the the physical network.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[ht]
\centering
\subfigure[Iterative deepening with three levels.] {
  \includegraphics[scale=0.4]{img/algorithms/iterative_deepening}
  \label{figure:dbfs:iterdeep}
}\qquad\qquad
\subfigure[Directed BFS.] {
  \includegraphics[scale=0.4]{img/algorithms/directed_bfs}
  \label{figure:dbfs:dbfs}
}\qquad\qquad
\subfigure[Local indices with radius size equal to $2$.] {
  \includegraphics[scale=0.4]{img/algorithms/local_indices}
  \label{figure:dbfs:localindx}
}
\caption{Improving search in P2P networks}
\label{figure:dbfs}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Gia}
\emph{Gia} \cite{chawathe_gia_2003} is an effort to solve the scalability
problem of the unstructured P2P file sharing systems, in particular Gnutella.
The main novelty in the design of Gia is the replacement of the blind flooding
approach of Gnutella with random walks \cite{lv_randomwalks_2002}. Although
random walks is a step in the right direction, issuing only a single copy of the
query within the network reduces the search scope, thus affecting negatively the
success rate of the query.  In order to overcome this limitation, Gia introduces
a token-based flow control mechanism, which is essentially an intelligent flow
control algorithm that gradually redirects the queries to nodes which are more
likely to answer. In order to prevent overloading of nodes with query requests,
Gia uses a token-based flow control algorithm in which each node announces the
number of query requests it can handle in terms of tokens to its neighbours, so
that neighbours only forward query requests to nodes that they previously
received tokens from. Gia also acknowledges the heterogenity in peer bandwidth,
processing power, disk speed, etc, of the nodes in P2P networks and uses this
information when connecting nodes to each other and by using a topology
adaptation algorithm, Gia ensures that high capacity nodes have high degrees and
low capacity nodes are within short proximity to high capacity ones.
% TODO: THIS FOLLOWING REMARK SOUNDS LIKE THE ALGORITHM SHOULDN'T BE IN THIS
%       SURVEY AFTER ALL!!
Although the topology adaptation algorithm Gia uses improves the scalability of
the network, it does not help much in solving the topology mismatch problem,
since it does not consider the underlying physical topology.

%
%More specifically, there are four key components in the design of
%\emph{Gia} which are summarized bellow:
%\begin{enumerate}
%  \item A \emph{dynamic topology adaptation} protocol that puts
%participating nodes within short reach of high capacity nodes so that these
%\emph{high-degree} nodes, which due to their high connectivity receive most of
%the queries, actually have the capacity to handle them.
%  \item An \emph{active flow control} scheme is used to avoid overloaded
% hot-spots. Heterogeneity is detected and flow control tokens are given to
%nodes based on the available capacity.
%  \item Every node maintains pointers to to the content that is offered by
% their immediate neighbours, creating a \emph{one-hop replication} of pointers,
%scheme.
%  \item A \emph{search protocol} based on random walks, that is biased towards
% directing queries to high-capacity nodes that are typically best able to
%answer these queries.
%\end{enumerate}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Distributed Cycle Minimization Protocol}
We have already discussed that blind flooding mechanism broadcasts messages with
no real targeting, many times to a direction far from the path that can
ultimatelly fullfil the query request. Another problem with topology unaware
systems is the duplication of messages due to cycles, even along the correct
forwarding path. The authors of \cite{zhu_dcmp_2008} fucused on that exact
deficiency of overlay networks and introduced Distributed Cycle Minimization
Protocol (DCMP), a dynamic, fully distributed method to remove cycles without
sacrificing overlay connectivity, resilience and other important properties of
unstructured architectures by avoiding a hierarchical organisation of peers. In
DCMP, once a cycle is detected, the most powerful node in that cycle is
elected as the \emph{Gate Peer} and the cycle is then broken at a strategic
place so that it will result in the minimisation of the distance between the
Gate Peer and all other nodes that participated in that cycle. The process
is managed by using two special message types namely \emph{Information
Collection (IC)} and \emph{Cut Message (CM)}. One disadvantage of DCMP is that
since the distance a forwarded message can travel is limited by the TTL value,
which is practically $7$ in most cases DCMP cannot detect cycles formed by more
than 7 peers. Even though cycle elimination improves the network performance, it
does not actually solve the topology mismatch problem.

%
%\subsection{Distributed Cycle Minimization Protocol}
%
%\paragraph{}
%The first step after detecting a duplicate message by some peer is to gather
% information from all peers in the cycle using a new type of control message
%called \emph{Information Collecting Message} or \emph{ICM}. ICM contains:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item a \emph{GUID}\footnote{Globally Unique IDentifier assigned to every
% query message generated by any node.} field same as the one of the duplicate
%message,
%  \item \emph{DetectionID} field which represents the direction of the
% connection where the duplicate was identified\footnote{This ensures the
%uniqueness of the ICM messages because as it travels through many cyclic paths,
%multiple peers will detect the duplicates and initiate an ICM message.}, and
%  \item \emph{Node Information Vector (NIV)} which contains information
% (bandwidth, CPU power, etc) about peers that propagated the ICM.
%\end{inparaenum}
%
%\paragraph{}
%Suppose $A$ detected the duplicate as depicted in Figure~\ref{figure:dcmp}. It
% then emits an ICM to $B$ and $F$, that initially contains information only
%about itself. Each peer that receives the ICM, appends its information and
%propagates it along the reverse path of the original message. Since two copies
%of ICM are sent, at some point, a peer, say peer $D$, will receive a duplicate
%ICM. Using the information in the NIVs of the ICMs, $D$, decides to cut (for
%example) the EF connection. To inform the other peers about its decision, it
%emits a \emph{Cut Message (CM)} which contains the GUID and DetectionID of the
%corresponding ICM and an additional field that identifies the connection to be
%cut. $D$, then, forwards the CM in the reverse directions from where the ICM
%arrived. Similarly CMs received by any peer are propagated toward the reverse
%path of the corresponding ICM. Eventually, either peer $E$ or peer $F$ will
%receive the CM and cut the connection, thus eliminating the cycle.
%
%Receiving a duplicate ICM denotes the existence of a cycle. The opposite is not
% true though. For example, if the cycle contains $2 \times TTL$ edges, it will
%not be detected, because the ICM messages will be discarded before they locate
%it. There is a tradeoff between preserving the connectivity of the network and
%minimizing the duplicates that makes such a possibility to be safely ignored.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
%\paragraph{}

%
% TODO: SOME DISCUSSION
%
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
%Experiments in \cite{zhu_dcmp_2008} showed that DCMP incurs a lower delay,
% returns more results and decreases the number of duplicate messages by 22\%,
%compared to LTM. Additionally DCMP has one to two orders of magnitude less
%overhead, because it adopts a more ``LAZY'' approach than broadcasting control
%messages periodically like LTM does.
%

@@

% These approaches include creating spanning trees using
%connection graphs, creating cluster of physically close nodes, or using latency
%information to detect proximity. The brief description of each category is
%presented below:
%
%  \begin{itemize}
%    \item \emph{Spanning tree based}. These approaches construct of a rich
%    graph  based on the network connections and build minimum spanning tree
%    on the graphs, causing large traffic overhead to the system
%    \cite{chu_esm_2000,chu_esm_2002}.
%
%    \item \emph{Cluster based}. These approaches select to link physically
%    closer nodes with each other, therefore shrink the search scope
%    significantly while mapping accuracy is not always guaranteed.
%
%    \item \emph{Minimum latency first}. Use of latency as a metric to calculate
%    distance among peers. They require global latency information
%    ``landmarks''\footnote{Measuring latency between peers and stable Internet
%    servers.}.
%
%  \end{itemize}

@@

\emph{Narada} \cite{chu_esm_2000,chu_esm_2001,chu_esm_2002} is a generic
protocol for creating self-adapting overlay networks, that can achieve
application-layer multicast communication without requiring IP multicast
infrastructure at the network layer\footnote{
  IP multicast is the term reffering to the method of sending IP datagrams to a
  group of receivers in a single transmission. Even though the method is
  available some years now, IP multicast has not taken off as anticipated since
  many believe that it violates the stateless design of the current Internet.
  For this reason it is widely deployed in contained environments like
  enterprises (i.e. IPTV applications - distance learning, video conferencing),
  commercial stock exchanges, and multimedia content delivery networks.
}. Although it was not originally designed as a P2P system nor can be considered
scalable in the contemporary sense of the term, Narada is considered pioneering
(maybe along with \emph{Scattercast} \cite{chawathe_scattercast_2000}) in that
it was the first to consider the feasibility of overlay-based, application
layer, services over the Internet that can take into account bandwidth and
latency properties of the physical underlying infrastructure. Additionally,
authors realised the inefficiency caused by the topology mismatch problem and
tried to encounter it by building a richer connected graph, called a
\emph{mesh}, and building per source minimum spanning trees\footnote{
  ENarada \cite{li_enarada_2008} used Gossip protocol for the construction
}
as shown in Figure~\ref{figure:narada}. They also keep the graph and the trees
dynamically updated while nodes continue to join and leave the network.
Moreover, the protocol tries to ease the physical link stress, the overall
resource usage and the relative delay among end systems. Unfortunately, the most
imporpant limitation of Narada is that although it works reasonably well for
small groups, it does not scale well for larger networks, therefore it is not
suitable for, potentially very large, P2P file sharing application networks.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Adaptive Overlay Topology Optimization and Adaptive Connection
Establishment}
\emph{Adaptive Overlay Topology Optimization (AOTO)} \cite{liu_aoto_2003} is one
of the first attempts, along with Narada, to address the topology mismatch
problem. AOTO is a distributed algorithm that works in two steps, namelly
\emph{Selective Flooding} and \emph{Active Topology} to optimize the usage of
the underlying physical resourses. In \emph{Selective Flooding} a minimum
spanning tree is built among each peer and its immediate neighbours so that
queries are not flooding the whole network and at the same time without
shrinking the search scope. During \emph{Active Topology}, the overlay
links are revised so that they depict the physical network topology as close as
possible. This is done independently, by each peer by replacing non-flooding
neighbours, with closer nodes. Picking a replacement out of these non-fooding
neighbours follows a random policy (called \emph{Randomized AT} algorithm in the
paper's context). For these steps a peer needs to keep track of communication
costs to all its neighbours (e.g. the network delay) as well as between any
pair of neighbours (meaning also that additional, cost probing, message types
need to be added to the Gnutella protocol). Whenever a new neighbour cost table
is received or there is a change of neighbours, the source peer has to
re-calculate the multicast tree and apply the randomized AT algorithm.

%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbours. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbours.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbours has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbour replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.

%
% TODO: REMAKE AAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAAA!!!!!!!!!!!!!!!!!!
%
 In
\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004}, the authors
extend the idea by introducing optimizations based on the depths of the minimum
spanning trees. But since the network delay is not always a reliable estimation
method to detect the physical location of peers, the algorithm still suffers
from the discrepancies caused by mislocated nodes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Location-aware Topology Matching}
\emph{Location-aware Topology Matching (LTM)} \cite{liu_ltm_2004} proposes a
method to optimize the overlay structure of the P2P network based on the
physical topology. To achieve this, peers issue special messages called
\textit{TTL-detector}s with TTL values of 0 and 1 so that the receiving peers
discover one- and two-hop neighbour sets ($N$ and $N^2$ respectively) around
them and calculating communication costs. Calculation is achieved through
timestamp checking, so clocks must be synchronised. The latency information
gathered is later used to evolve the overlay network into a more efficient one,
without reducing the search scope. Each node examines the latency information
among his direct neighbours and those with larger latency are put in to a
will-cut list where they remain for a certain period of time until when they are
ultimatelly cut and recorded to the peer's cut list. Thus, low productive
connections are dropped and replaced by more efficient ones, reducing the
latency on the overall network. Although LTM improves the overall efficiency of
the P2P network, it does not actually use real physical topology information,
just latency metrics, therefore it does not offer a guaranteed safety net for
the topology mismatch problem.

%
% TODO: SOME DISCUSSION
%
%\paragraph*{Low productive connection cutting}
%There are three cases for any peer $P$ who receives $d(i, S, v)$ multiple
% times:
%\begin{inparaenum}[\itshape i\upshape)]
%  \item $P$ receives both $d(i, S, 1)$ and $d(i, S, 0)$
%  \item $P$ receives multiple $d(i, S, 0)$s from different paths, and P
% randomly chooses to process one
%  \item $P$ receives one $d(i, S, 1)$ and multiple $d(i, S, 0)$s, and $P$
% processes $d(i, S, 1)$ and one randomly selected $d(i, S, 0)$
%\end{inparaenum}
%If the link with the largest cost is found and is a direct neighbour then the
% connection is put in a will-cut list and stays there for a certain period of
%time. If it is not, then it is handled by other peers. After that period,
%connections are cut and recorded to $P$'s cut-list.
%
%\paragraph*{Source probing}
%For a peer $P\in(N^2(S) - N(S))$ who receives only one $d(i, S, 0)$, the cost
% of $PS$ is obtained (with list look-up or probing). Then $P$ compares it with
%the cost from each hop and if $PS$ has the largest cost, $P$ will not keep this
%connection, while otherwise the connection will be created.
%
%\paragraph{}
%Supposing $n$ is the number of peers, $c_n$ is the average number of neighbours
% and $c_e$ is the average cost of logical links, then in the flooding-based
%search the traffic incurred by one query from an arbitrary peer in a
%peer-to-peer network is $O(n)$. As observed in the Gnutella network
%\cite{sripanidkulchai_gnutella_2001}, each peer issues $0.3$ queries per minute
%in average, thus the per minute traffic incurred by the network with $n$ peers
%is $O(n^2)$. Because each $d(i, S, v)$ has a TTL of $2$ in each source peer,
%the traffic for one time LTM optimization in all peers is at most $2nc_n^2c_e$.
%If each peer uses LTM $k$ times per minute, the total traffic incurred is
%$2knc_n^2c_e$. Simulation shows the best value for $k$ is $2$ or $3$. So, the
%traffic overhead caused by LTM to the network is $O(n)$.
%
%TTLj-detectors, with $j > 2$, would detect and break cycles with more than 4
% links. LTM though, does not use such detectors because detector-flood traffic
%would increase significantly, and cut links between two end-peers, could cause
%queries initiated by them to traverse a path much more expensive than the cost
%on the the cut link.
%
%\paragraph{}
%LTM disadvantages are
%\begin{inparaenum}[\itshape i\upshape)]
%  \item disagreement of measured delay due to unsynchronized clocks causes
% problems when deciding the cut positions, which can influence the network
%connectivity, and
%  \item the network delay metric mainly focuses on disabling the connections
% between peers physically far away without considering the shortcuts created by
%powerful peers.
%\end{inparaenum}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Scalable Bipartite Overlay}
\emph{Scalable Bipartite Overlay (SBO)}
\cite{liu_bipartite_IPDPS,liu_bipartite_2007} reduces the overhead of
creating and maintaining a minimum spanning tree cost by randomly dividing the
nodes into two groups, namely red and white and assigning different tasks to
different groups. When a peer joins the network, is randomly assigned with an
initial colour, say red or white (separating all peers into two groups). Then
the peer that plays the role of the bbootstrap host provides the joining peer
with a list of active peers along with their colour information. The later uses
this list to establish connections to differently coloured peers. This way, all
peers form a bipartite overlay. The white peers measure distances to
neighbours (red only) by using the network delay as a metric and report their
corresponding red neighbours. The red peers, equipped with the information of
all two-hop neighbours ($N^2$), creates minimum spanning tree of these
neighbours and assigns efficient forwarding paths. Having a minimum spanning
tree with two hops, a red peer is able to send its queries within that range.
Some white peers, though, have become non-forwarding neighbours. In this phase,
such a (white) neighbour will try to find another red peer being two hops away
from its current red neighbour to replace the later as its new neighbour. The
white peers can further optimize their positions within the overlay if this is
required.

%
% TODO: SOME DISCUSSION
%
%In a static enviromnent LTM may reduce traffic cost by around 80 to 85 percent
% while SBO reduces traffic cost between 85 and 90 percent. However, LTM  is
%proved to converge in around 2-3 steps while SBO needs 4-5 steps. Moreover LTM
%reduces response time by more than 60 percent in 3 steps while SBO needs 8. In
%a dynamic environment (10 minute average peer lifetime, 0.3 queries/sec by each
%peer) SBO and LTM reduce the average traffic cost per query (including the
%overhead due to the optimization steps) by 85 and 80 percent, respectively.
%Moreover LTM reduces the response time per query to 30 percent while SBO to 35
%percent.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Adaptive Connection Establishment (ACE)}
\emph{Adaptive Connection Establishment (ACE)} \cite{liu_ace_2004} builds an
overlay multicast tree among each source node and the peers within a certain
diameter from the source peer and optimizes the neighbour connections that are
not in that tree. To achieve that it calculate cost between nodes using network
delay as a metric. Each peer probes the costs with its immediate logical
neighbours and forms a \emph{neighbour cost table (NCT)} using a special
routing message type. Two neighbouring peers exchange their NCTs in order for
every peer to obtain the cost between any pair of its local neighbours forming a
small overlay topology. Moreover, based on obtained NCTs a minimum spanning tree
among each peer and its immediate neighbours is built. Ultimately, physically
far away neighbours are replaced by physically close ones. Specifically, a peer
$S$ probes the distance between one of its non-flooding neighbour's neighbour,
say $G$ and $H$ respectively. Assuming that the link to the neighbour's neigbour
($SH$) is smaller that that of the neighbour ($SG$), the later is cut and a new
connection is established. In the oposite situation where $SG$ is smaller than
$SH$ then if $SH$ is smaller that $GH$ then $H$ is preserved as $S$'s new
neighbour. In the case where $SH$ is larger than $SG$ and $GH$, no connection
will be established and $S$ will continue probing another neighbour's neighbour.
The above optimisation is conducted within $1$-neighbour closure (among its
source peer and all its direct neighbours) but the scope can be extended. The
larger the scope, the better topology matching improvement but also the greater
the computational overhead.

%
% TODO: SOME DISCUSSION
%
%Simulations in \cite{liu_acesims_2004} show that the average scope of each
% query to cover the same scope of nodes is reduced by about 65 percent without
%losing any autonomy feature, while the average response time can be reduced by
%35 percent. Larger diameter topologies lead to better topology optimization
%rate but also to higher communication and computation overhead. It was also
%found that it is more effective in higher connectivity dense topologies.
%Compared to LTM, it comes short of convergence speed. In
%\cite{ni_mismatch_2004} shows reduction of both total traffic (90 percent) and
%response time (80 percent) to message queries without shrinking the search
%scope. SBO, on the other hand, achieves approximately 85 percent reduction on
%traffic cost and about 60 percent reduction on query response time. Last but
%not least, it is concluded that work must be done on incorporating a more
%sophisticated selection policy for candidate non-flooding peers.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph*{\bf Hops Adaptive Neighbour Discovery (HAND)}
\cite{chen_hand_2006} proposes the \emph{HAND} algorithm which uses a
fully distributed triple hop adjustment strategy to address the topology
mismatch problem. The approach's ultimate goal is to shape the current overlay
graph $G$ into the \emph{Logical Communication Network (LCN)} $G^{*}$ which is
how the optimal overlay is refered in the paper's context. A formal
definition of achieving the above match is only if all peer hop sequences $(v_1,
v_2, \ldots, v_k)$ in $G$ exist in $G^{*}$ and in the same order\footnote{In
practice triple sequences $(v_1, v_2, v_3)$ are used.}. The mismatching
detection is done in the following way. Suppose we want to verify peer a
sequence, say $v_2-v_1-v_3$. A pair of probing messages are sent from $v_1$ to
$v_2$ and $v_3$. Suppose delays of $(v_1,v_2)$ and $(v_1,v_3)$ are are denoted
as $x$ and $z$, respectively. When the probing message arrives to $v_2$ it
forwards it directly to $v_3$. Similarly, when the probing message arrives to
$v_3$, it forwards it directly to $v_2$. These last steps are performed in order
to obtain delays of $(v_2,v_3)$ and $(v_3,v_2)$ physical paths, respectively,
denoted by $y$. If $y=z-x\pm\varepsilon$, sequence $v_2-v_1-v_3$ is mismatched
and should be adjusted to $v_1-v_2-v_3$ by deleting edge $(v_1,v_3)$ and adding
a new $(v_2,v_3)$. If $y=x-z\pm\varepsilon$, sequence $v_2-v_1-v_3$ is
mismatched and should be adjusted to $v_1-v_3-v_2$ by deleting edge $(v_1,v_2)$
and adding a new $(v_3,v_2)$, where $\varepsilon$ is a small positive real
number denoting additional delays caused by possible forwarding and jitter
delays. The advantages of the HAND algorithm compared to other approaches are
that:
\begin{inparaenum}[\itshape i\upshape)]
  \item it does not need any clock synchronization,
  \item it is a fully distributed algorithm making it robust and reliable in
        decentralized systems,
  \item the traffic overhead of the triple hop adjustment is very low,
  \item it is applicable to dynamic peer-to-peer environments, and
  \item maintains lower query response time.
\end{inparaenum}

%
% TODO: SOME DISCUSSION
%
%Measurements conducted for evaluation perposes showed that in a static
% environment the algorithm can effectively decrease traffic cost by about 77
%percent and shorten the query response time by about 49 percent in less than
%two minutes. In a dynamic environment it shows similar behaviour and with the
%size of the overlay network having little impact on the effectiveness of the
%algorithm. Compared to LTM both algorithms have almost the same traffic
%reduction rate, however on the response time reduction rate HAND has a higher
%one by about 4 percent. The traffic overhead of HAND is much less than that of
%LTM by an average of 55 percent.

@@

\hline
\textbf{MAY OMIT - I CHANGED IT TO STRUCTURED SINCE THERE IS A REFERENCE FOR
DHT (OF COURSE IT MIGHT POSIBLE TO BE APPLIED TO BOTH. MAYBE NEED TO CHECK) -
T2MC} &
\textbf{Overlay optimization based} Uses traceroute results for clustering the
nodes  & & \\
